---
title: "Discursos Presidenciales"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(tm)
library(wordcloud)

txt <- readLines("data/00.txt",encoding="UTF-8")
txt = iconv(txt, to="ASCII//TRANSLIT")
corpus <- Corpus(VectorSource(txt))
d  <- tm_map(corpus, tolower)
d  <- tm_map(d, stripWhitespace)
#d <- tm_map(d, removePunctuation)
d <- tm_map(d, removeWords, stopwords("spanish"))
tdm <- TermDocumentMatrix(d)

findFreqTerms(tdm, lowfreq=20)

```

## Including Plots

You can also embed plots, for example:
```{r}
m <- as.matrix(tdm)
v <- sort(rowSums(m),decreasing=TRUE)
df <- data.frame(word = names(v),freq=v)
```


```{r pressure, echo=FALSE, warning=FALSE}
wordcloud(df$word,df$freq,min.freq=6)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


